Influence of Time Integration Methodology on Double Detonation Type Ia Supernova Nucleosynthesis

### 2023-06-23 subch_tols/paper.tex
more work

We run 3 different types of integration methods: traditional operator
splitting, using Strang splitting, both with integration of the energy
equation and without any temperature evolution during the burn.  \MarginPar{comment about the EOS}.  These methods are compared to the simplified-SDC integtation.

@@

We also vary the CFL number and the integration tolerances.

>>>>

We run 3 different types of integration methods: traditional operator
splitting, using Strang splitting, both with integration of the energy
equation and without any temperature evolution during the
burn.  \MarginPar{comment about the EOS}.  These methods are compared
to the simplified-SDC integtation.  We also vary the CFL number and
the integration tolerances.

@@

To understand the difference in the \isot{Ni}{56} mass between the SDC and Strang simulations at 
CFL = 0.2,

\begin{figure}[t]
\centering
\plotone{sdc_strang_compare_abar_summary_plot}
\caption{\label{fig:abar_sdc_strang} Comparison of the mean molecular weight between SDC and Strang (both run with CFL = 0.2) at $t = 0.2~\mathrm{s}$.}
\end{figure}
